Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-21 WSSSPE3/report/WSSSPE3_review.tex
Keynote: fix typos and add more details.

>>>>

In his keynote address, Turk recapped the course of development of WSSSPE
workshops alongside with his career from a postdoc to an academic over the past
few years. The first WSSSPE workshop was at the Supercomputing Conference (SC13)
in 2013, but he observed that the notion of sustainable scientific software drew
in an audience beyond supercomputing. In the following year, WSSSPE1.1 at SciPy
had speakers talking about how software has been sustained inside the scientific
Python community. WSSSPE2 at SC14 had breakout group discussions coming up with
actionable items, and WSSSPE2.1 at SciPy 2015 was similar. Turk noted the
different atmosphere and approaches of the surrounding large conferences,
despite similar WSSSPE participants. WSSSPE3 broke free of the Supercomputing
Conference environment this time, and in Turk's words, it spoke to the fact that
scientific software comes from many different types of inquiries, deployment,
strategies for maintenance, users; and ways of measuring the value of a piece of
software. It appeared to Turk that the supercomputing conferences generally
adopt some top-down approaches, whereas SciPy bottom-up systems; the essential
messages perceived were also often circumpolar: software getting harder in
supercomputing communities, but software becoming better in the SciPy groups.

%preconceptions
